Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching

### 2019-01-31 supCLT.tex
supCLT.tex: 1115b

    There exists $\gamma_0 \in [0,\beta)$ close enough to $\beta$ such that for each $\gamma_0 \leq \gamma < \beta$, $\alpha\gamma>|p|(1+\gamma)b$.
    Using  Lemma \ref{lemma24} and the fact $\kappa_{\phi_p}=|p|$, we get that, there exists a constant $C_{\gamma, \mu, p}>0$ (which depends on the choice of $\gamma$, $\mu$ and $p$)  such that
 $$
 	\|H_t^p\|_{\mathbb P_\mu;1+\gamma}
    \leq C_{\gamma, \mu, p} e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}
    =C_{\gamma, \mu, p}, \quad t\geq 0.
 $$
    For any $0\leq\gamma<\gamma_0$, note that
$$
	\|H_t^p\|_{\mathbb P_\mu;1+\gamma}
	\leq\|H_t^p\|_{\mathbb P_\mu;1+\gamma_0}
	<C_{\gamma_0, \mu, p},
	\quad t\geq 0.
$$

    Hence, for each $\gamma \in (0,\beta)$, the martingale is bounded in $L_{1+\gamma}(\mathbb{P}_{\mu})$ and this indicates the convergence in $L_{1+\gamma}(\mathbb{P}_{\mu}) $ and almost sure,
%added
    according to \cite[Theorem 5.4.5]{Durrett2010Probability}.
%end added
\end{proof}

\deleted{
    Recall that $\|X_t\|=\langle 1,X_t\rangle$.
    By Lemma \ref{lemma26},
    %it is not to hard to prove that,
    it is clear that,
    under $\mathbb{P}_{\mu}$, the process $W_t=e^{-\alpha t}\|X_t\|$ is a positive martingale satisfying
$\lim_{t\rightarrow \infty} W_t= W_{\infty},$
$\mathbb{P}_{\mu}$-a.s and in $L^{1+\gamma}(\mathbb{P}_{\mu})$. So $W_{\infty}$ is non-degenerate and the $(1+\gamma)$-th moment is finite. Moreover,  we have $\mathbb{P}_{\mu}(W_{\infty})=\|\mu\|$ and $\{W_{\infty}=0\}=D,$ $\mathbb{P}_{\mu}$-a.s.

%comment
    {\bf Zhenyao: we need references for the last assertion. Also, we used three different notation $M, H$ and $W$ to denote one martingale. This is unnessary.}
    }
%end comment
\added{
In particular, when $p=0$, $H_t^0$ reduces to $H_t:=e^{-\alpha t}\|X_t\|$, thus, as $t\rightarrow \infty$, $H_t$ convergences to $H_{\infty}$ $\mathbb{P}_{\mu}$-a.s and in $L_{1+\gamma}(\mathbb{P}_{\mu})$.}
\begin{lem}\label{lem: control of Wt}
 %For any $\gamma\in [0,\beta)$ and $0\leq s<t$, we have
 For any $\gamma\in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exists a $C> 0$ such that for each $0\leq s<t$,
 $$\|H_t-H_s\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{-\alpha s/2}.$$
\end{lem}

\begin{proof}
%new added
     Fix $\gamma \in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
    According to Lemma \ref{lem: control of mgtrs}, there exists a constant $C_0>0$, such that for each $0\leq r\leq s $ with $s-r\leq1$, we have
    \begin{align}
        \mathbb{P}_{\mu}\big[\big|e^{\alpha(t-s)}\|X_s\|-e^{\alpha(t-r)}\|X_r\|\big|^{1+\gamma}\big]
        \leq C_0e^{\alpha t+(t-s)\alpha\gamma}.
    \end{align}
    Dividing both sides by $e^{\alpha t(1+\gamma)}$, we get
    \begin{align}
        \mathbb{P}_{\mu}\left|H_s-H_r\right|^{1+\gamma}\leq  C_0 e^{-\alpha \gamma s}.
    \end{align}
    Then there is a $C>0$, for any $0\leq s<t$,
\begin{align}
	& \|H_t-H_s\|_{\mathbb{P}_{\mu};1+\gamma}
	\leq \|H_{\lfloor s \rfloor+1}-H_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}\|H_{k+1}-H_{k}\|_{\mathbb{P}_{\mu};1+\gamma}+\|H_t-H_{\lfloor t \rfloor+1}\|_{\mathbb{P}_{\mu};1+\gamma}
	\\& \leq C_0^{\frac{1}{1+\gamma}} \Big(e^{-\frac{\alpha \gamma s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{\alpha \gamma k}{1+\gamma}}+ e^{-\frac{\alpha \gamma t}{1+\gamma}}\Big)
	\leq Ce^{-\frac{\alpha \gamma}{1+\gamma}s}\leq Ce^{-\frac{\alpha}{2}s}.
\end{align}	
\end{proof}

\added{Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$. According to \cite[Example 3.1]{Li2011Measure-valued}, we have
\begin{align}\label{CSBP}
    \mathbb{P}_{\mu} [e^{-\lambda\|X_t\|}]
    =e^{-\|\mu\|v_t(\lambda)},
    \quad \lambda \geq 0, t\geq 0,
\end{align}
    where
\[
    v_t(\lambda)=\frac{\alpha^{1/\beta}}{(\alpha\lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha \beta t})^{1/\beta}},\quad t\geq 0,\lambda\geq 0.
\]

     Recall that the extinction probability of the superprocess is $\mathbb{P}_{\mu}(D)=e^{-\alpha^*\|\mu\|}$ where $\alpha^*=\alpha^{1/\beta}$ is the larger roots of $\psi(z)=0$}.
    Denote by $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
    By \eqref{CSBP} and the markovian property we have for each $\mu \in \mathcal M_c(\mathbb R^d), \lambda \geq 0$ and
    $t\geq 0$,

\begin{align}
    \label{laplaceexpress}
    \mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|}]
    &=\frac{ \mathbb P_\mu[e^{-\lambda \|X_t\| }\mathbb P_\mu(D^c| \mathscr F_t)] }{\mathbb P_\mu(D^c)}
    =\frac{ \mathbb P_\mu[e^{-\lambda \|X_t\| }(1-e^{-\alpha^*\|X_t\|})] }{\mathbb P_\mu(D^c)}
    \\&=\frac{e^{-\|\mu\|v_t(\lambda)}-e^{-\|\mu\|v_t(\lambda+\alpha^*)}}{1-e^{-\|\mu\|\alpha^*}}
    \leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|.
\end{align}

@@

\begin{proof}
 By Chebyshev's Inequality and formula \eqref{laplaceexpress}, we get

@@

In this section, we will prove the main results of this paper. Recall that $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$ and let $F_k(\nu)=\left(e^{\alpha k}\|\nu\|\right)^{\frac{1}{1+\beta}},~ \nu\in \mathcal{M}(\mathbb{R}^d)$.
\begin{comment}
\begin{lem}\label{lemma31}
For any $x,y\in \mathbb{C}$, $|e^x-e^y|\leq (e^{Re(x)}\vee e^{Re(y)})|x-y|$.
\end{lem}
\begin{proof}
let $z=Re(y)+iIm(x)$,
\begin{align}\label{estim}
    |e^x-e^y|\leq|e^x-e^z|+|e^z-e^y|\leq |e^{Re(x)}-e^{Re(y)}|+e^{Re(y)}|x-y|\leq (e^{Re(x)}\vee e^{Re(y)})|x-y|.
\end{align}
\end{proof}
\end{comment}

\begin{lem}\label{lemma32}
Recall $\mathcal{A}_t(\epsilon)=\{\|X_t\|\in\|\mu\|(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t})\},~\epsilon,t>0$, then for any $\epsilon>0$, we have
\begin{align}
    \lim_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)=D^c, ~~\mathbb{P}_{\mu}\text{-}{\rm a.s}.
\end{align}
\end{lem}
\added{
\begin{proof}
    We just need to prove
    \begin{align}
        D^c \subset \liminf_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)\subset \limsup_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)\subset D^c,~~\mathbb{P}_{\mu}\text{-}{\rm a.s}.
    \end{align}
    for any $\omega\in D$, there exists $S>0$, such that $\|X_t(\omega)\|=0,~t\geq T$. Thus $\omega \notin \cup_{t\geq S}\mathcal{A}_t(\epsilon)$ and $\omega\notin  \limsup_{t\rightarrow\infty}\mathcal{A}_t(\epsilon):=\cap_{S\geq 0}\cup_{t\geq S}\mathcal{A}_t(\epsilon)$ imply that $\limsup_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)\subset D^c$.

    For any $\omega \in \{H_{\infty}>0\}\cap\{\lim_{t\rightarrow \infty} H_t=H_{\infty}\}$, there exists $\delta>0$ such that $H_{\infty}(\omega)\in(\delta,\frac{1}{\delta})$ and there exists $S_1>0$ such that for any $t\geq S_1$, we have $\frac{\delta}{2}\leq H_t(\omega)\leq 2\delta,$. Taking $S_2>0$ such that for any $t>S_2$, $\|\mu\|e^{-\epsilon t}<\frac{\delta}{2}$ and $\|\mu\|e^{-\epsilon t}>2\delta$, then $\omega\in \mathcal{A}_t(\epsilon),~t>S:=\max\{S_1,S_2\}$ implies $\omega \in \liminf_{t\rightarrow \infty}\mathcal{A}_t(\epsilon):=\cup_{S>0}\cap_{t\geq S}\mathcal{A}_t(\epsilon)$.

    According to \cite{LSR}, $D^c=\{H_{\infty}>0\}~ \mathbb{P}_{\mu}$-a.s, combining with the fact $\lim_{t\rightarrow \infty}H_t=H_{\infty}~\mathbb{P}_{\mu}$-a.s, we get the result.
\end{proof}
}
\begin{lem}\label{lemma33}

 Let $f\in \mathcal{P}$, assume that $\alpha\beta\leq \kappa_fb(1+\beta)$, then for any  $k\in\mathbb{N}$ and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
 \begin{align}
      \frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
 \end{align}
 where $\zeta_k$ is a $(1+\beta)$-stable random variable with characteristic function
 $$\mathbb{E}e^{i\theta\zeta_k}=\exp\left[e^{\alpha}m_k[\theta f]\right].$$
 \end{lem}

 \begin{proof}
For each $\theta \in \mathbb{R}$, let $\tilde{\theta}_{t,k}=\frac{\theta}{F_k(X_{t-k-1})}$. For any $k\in\mathbb{N}$ and $t>k+1$, we have
         \begin{align}
        &\mathbb{P}_{\mu}\big[\exp(i\theta\frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})\big|\mathscr{F}_{t-k-1}\big]\\
        &=\exp\big(\langle U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-i\tilde{\theta}_{t,k}\langle T_{k+1}^{\alpha}f, X_{t-k-1}\rangle\big).\\
        \label{condition mean}
        &=\exp\big(\langle U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle+\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle\big)\\
       \end{align}
         Fix $\gamma_0\in (0,\beta)$, let $p=\min\{b,\frac{\alpha\gamma_0}{2(1+\gamma_0)}\}$ and $\epsilon_0=\min\{\frac{\alpha\beta}{2(1+2\beta)},\frac{p}{2}\}$.
       To get the conclusion of Lemma \ref{lemma33}, it suffices to show that
       \begin{align}
           \mathbb{P}_{\mu}\Big(\exp(i\theta\frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1}}))\mathbf{1}_{D^c}\Big)\xrightarrow{t\rightarrow \infty}\mathbb{P}_{\mu}(D^c)\exp(e^{\alpha}m_k[\theta f]).
       \end{align}
     Equivalently, by Lemma \ref{lemma32}, we just need to prove
     \begin{align}
        \Big|\mathbb{P}_{\mu}\Big[\big(\exp(i\theta \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big]\Big|\xrightarrow{t\rightarrow\infty} 0.
    \end{align}
      According to \eqref{condition mean},
    \begin{align}
        &\Big|\mathbb{P}_{\mu}\Big[\big(\exp(i\theta \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big]\Big|\\
        &=\Big|\mathbb{P}_{\mu}\Big[\mathbb{P}_{\mu}\Big(\big(\exp(i\theta \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big|\mathscr{F}_{t-k-1}\Big)\Big]\Big|\\
        &\leq \mathbb{P}_{\mu}\big[\big|\langle U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f), X_{t-k-1}\rangle\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]\\
        \label{ineqinlem31}
        &+\mathbb{P}_{\mu}\big[\big|\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[\theta f]\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big].
    \end{align}
Step 1.  We will show that for each $\mu \in\mathcal{M}_c(\mathbb{R}^d)$, there exists $C>0$, such that for any $\theta\in \mathbb{R}$, $k\in\mathbb{N}$ and $t>k+1$,
    \begin{align}
    \label{lemma31q}
        \mathbb{P}_{\mu}\big[\big|\langle  U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f), X_{t-k-1}\rangle\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]\leq C|\theta|^{1+2\beta}e^{-\frac{\alpha\beta}{2(1+\beta)}(t-k-1)}.
    \end{align}
Let $(R,S)$ be the $(1+2\beta)$-control-pair in Lemma \ref{lem: upper bound for usgx} (6). For any $\theta\in\mathbb{R}$, $k \in \mathbb N$ and $t>k+1$, we have
\begin{align}

>>>>

    There exists $\gamma_0 \in [0,\beta)$ close enough to $\beta$ such that for each $\gamma_0 \leq \gamma < \beta$, $\alpha\gamma>|p|(1+\gamma)b$.
    Using  Lemma \ref{lem: control moment} and the fact $\kappa_{\phi_p}=|p|$, we get that, there exists a constant $C_{\gamma, \mu, p}>0$ (which depends on the choice of $\gamma$, $\mu$ and $p$)  such that
 $$
 	\|H_t^p\|_{\mathbb P_\mu;1+\gamma}
    \leq C_{\gamma, \mu, p} e^{-(\alpha-|p|b)t}e^{(\alpha-|p|b)t}
    =C_{\gamma, \mu, p}, \quad t\geq 0.
 $$
    For any $0\leq\gamma<\gamma_0$, note that
$$
	\|H_t^p\|_{\mathbb P_\mu;1+\gamma}
	\leq\|H_t^p\|_{\mathbb P_\mu;1+\gamma_0}
	<C_{\gamma_0, \mu, p},
	\quad t\geq 0.
$$

    Hence, for each $\gamma \in (0,\beta)$, the martingale is bounded in $L_{1+\gamma}(\mathbb{P}_{\mu})$ and this indicates the convergence in $L_{1+\gamma}(\mathbb{P}_{\mu}) $ and almost sure,
    according to \cite[Theorem 5.4.5]{Durrett2010Probability}.
\end{proof}

In particular, when $p=0$, $H_t^0$ reduces to $H_t:=e^{-\alpha t}\|X_t\|$, thus, as $t\rightarrow \infty$, $H_t$ convergences to $H_{\infty}$, $\mathbb{P}_{\mu}$-a.s and in $L_{1+\gamma}(\mathbb{P}_{\mu})$.
\begin{lem}\label{lem: control of Wt}
 %For any $\gamma\in [0,\beta)$ and $0\leq s<t$, we have
 For any $\gamma\in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$, there exists a $C> 0$ such that for each $0\leq s<t$,
 $$\|H_t-H_s\|_{\mathbb{P}_{\mu};1+\gamma}\leq C e^{-\alpha s/2}.$$
\end{lem}

\begin{proof}
%new added
     Fix $\gamma \in (0,\beta)$ and $\mu\in \mathcal M_c(\mathbb R^d)$.
    According to Lemma \ref{lem: control of mgtrs}, there exists a constant $C_0>0$, such that for each $0\leq r\leq s $ with $s-r\leq1$, we have
    \begin{align}
        \mathbb{P}_{\mu}\big[\big|e^{\alpha(t-s)}\|X_s\|-e^{\alpha(t-r)}\|X_r\|\big|^{1+\gamma}\big]
        \leq C_0e^{\alpha t+(t-s)\alpha\gamma}.
    \end{align}
    Dividing both sides by $e^{\alpha t(1+\gamma)}$, we get
    \begin{align}
        \mathbb{P}_{\mu}\left|H_s-H_r\right|^{1+\gamma}\leq  C_0 e^{-\alpha \gamma s}.
    \end{align}
    Then there is a $C>0$, for any $0\leq s<t$,
\begin{align}
	& \|H_t-H_s\|_{\mathbb{P}_{\mu};1+\gamma}
	\leq \|H_{\lfloor s \rfloor+1}-H_s\|_{\mathbb{P}_{\mu};1+\gamma}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}\|H_{k+1}-H_{k}\|_{\mathbb{P}_{\mu};1+\gamma}+\|H_t-H_{\lfloor t \rfloor+1}\|_{\mathbb{P}_{\mu};1+\gamma}
	\\& \leq C_0^{\frac{1}{1+\gamma}} \Big(e^{-\frac{\alpha \gamma s}{1+\gamma}}+\sum_{k=\lfloor s \rfloor+1}^{\lfloor t \rfloor}e^{-\frac{\alpha \gamma k}{1+\gamma}}+ e^{-\frac{\alpha \gamma t}{1+\gamma}}\Big)
	\leq Ce^{-\frac{\alpha \gamma}{1+\gamma}s}\leq Ce^{-\frac{\alpha}{2}s}.
    \qedhere
\end{align}	
\end{proof}

\deleted{
Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$. According to \cite[Example 3.1]{Li2011Measure-valued}, we have
\begin{align}\label{CSBP}
    \mathbb{P}_{\mu} [e^{-\lambda\|X_t\|}]
    =e^{-\|\mu\|v_t(\lambda)},
    \quad \lambda \geq 0, t\geq 0,
\end{align}
    where
\[
    v_t(\lambda)=\frac{\alpha^{1/\beta}}{(\alpha\lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha \beta t})^{1/\beta}},\quad t\geq 0,\lambda\geq 0.
\]
    Recall that the extinction probability of the superprocess is $\mathbb{P}_{\mu}(D)=e^{-\alpha^*\|\mu\|}$ where $\alpha^*=\alpha^{1/\beta}$ is the larger roots of $\psi(z)=0$.
    Denote by $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
    By \eqref{CSBP} and the markovian property we have for each $\mu \in \mathcal M_c(\mathbb R^d), \lambda \geq 0$ and
    $t\geq 0$,

\begin{align}
    \label{laplaceexpress}
    \mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|}]
    &=\frac{ \mathbb P_\mu[e^{-\lambda \|X_t\| }\mathbb P_\mu(D^c| \mathscr F_t)] }{\mathbb P_\mu(D^c)}
    =\frac{ \mathbb P_\mu[e^{-\lambda \|X_t\| }(1-e^{-\alpha^*\|X_t\|})] }{\mathbb P_\mu(D^c)}
    \\&=\frac{e^{-\|\mu\|v_t(\lambda)}-e^{-\|\mu\|v_t(\lambda+\alpha^*)}}{1-e^{-\|\mu\|\alpha^*}}
    \leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|.
\end{align}
}

\added{Write $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.}

@@

\begin{proof}
\added{
    Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$. According to \cite[Example 3.1]{Li2011Measure-valued}, we have
\begin{align}\label{CSBP}
    \mathbb{P}_{\mu} [e^{-\lambda\|X_t\|}]
    =e^{-\|\mu\|v_t(\lambda)},
    \quad \lambda \geq 0, t\geq 0,
\end{align}
    where
\[
    v_t(\lambda)=\frac{\alpha^{1/\beta}}{(\alpha\lambda^{-\beta}e^{-\alpha \beta t}+1-e^{-\alpha \beta t})^{1/\beta}},\quad t\geq 0,\lambda\geq 0.
\]
    Recall that the extinction probability of the superprocess is $\mathbb{P}_{\mu}(D)=e^{-\alpha^*\|\mu\|}$ where $\alpha^*=\alpha^{1/\beta}$ is the larger roots of $\psi(z)=0$.
    Denote by $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$.
    By \eqref{CSBP} and the markovian property we have for each $\mu \in \mathcal M_c(\mathbb R^d), \lambda \geq 0$ and
    $t\geq 0$,

\begin{align}
    \label{laplaceexpress}
    \mathbb{\tilde{P}}_{\mu}[e^{-\lambda \|X_t\|}]
    &=\frac{ \mathbb P_\mu[e^{-\lambda \|X_t\| }\mathbb P_\mu(D^c| \mathscr F_t)] }{\mathbb P_\mu(D^c)}
    =\frac{ \mathbb P_\mu[e^{-\lambda \|X_t\| }(1-e^{-\alpha^*\|X_t\|})] }{\mathbb P_\mu(D^c)}
    \\&=\frac{e^{-\|\mu\|v_t(\lambda)}-e^{-\|\mu\|v_t(\lambda+\alpha^*)}}{1-e^{-\|\mu\|\alpha^*}}
    \leq \frac{\|\mu\|}{1-e^{-\|\mu\|\alpha^*}}\left|v_t(\lambda)-v_t(\lambda+\alpha^*)\right|.
\end{align}
}

By Chebyshev's Inequality and formula \eqref{laplaceexpress}, we get

@@

In this section, we will prove the main results of this paper. Recall that $\mathbb{\tilde{P}}_{\mu}=\mathbb{P}_{\mu}(\cdot|D^c)$ and let $F_k(\nu)=\left(e^{\alpha k}\|\nu\|\right)^{\frac{1}{1+\beta}},~ \nu\in \mathcal{M}(\mathbb{R}^d)$.

\begin{lem}\label{lemma32}
    \deleted{Recall} \added{Write} $\mathcal{A}_t(\epsilon)=\{\|X_t\|\in\|\mu\|(e^{(\alpha-\epsilon)t},e^{(\alpha+\epsilon)t})\},$ for each $\epsilon,t>0$. 
    Then for any $\epsilon>0$, we have
\begin{align}
    \lim_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)=D^c, ~~\mathbb{P}_{\mu}\text{-}{\rm a.s}.
\end{align}
\end{lem}
\added{
\begin{proof}
    We just need to prove
    \begin{align}
        D^c \subset \liminf_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)\subset \limsup_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)\subset D^c,~~\mathbb{P}_{\mu}\text{-}{\rm a.s}.
    \end{align}

    On one hand, let $\omega\in D$. Then there exists $T(\omega)>0$, such that $\|X_t(\omega)\|=0,$ for each $t\geq T(\omega)$. 
    Thus $\omega\notin  \limsup_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)=\cap_{s\geq 0}\cup_{t\geq s}\mathcal{A}_t(\epsilon)$.
    This implies that $\limsup_{t\rightarrow\infty}\mathcal{A}_t(\epsilon)\subset D^c$.

    On the other hand, let $\omega \in \{H_{\infty}>0\}\cap\{\lim_{t\rightarrow \infty} H_t=H_{\infty}\}$. 
    Then, there exists $\delta>0$ such that $H_{\infty}(\omega)\in(\delta,\frac{1}{\delta})$ and there exists $S_1>0$ such that for any $t\geq S_1$, we have $\frac{\delta}{2}\leq H_t(\omega)\leq 2\delta$. 
    Taking $S_2>0$ such that for any $t>S_2$, $\|\mu\|e^{-\epsilon t}<\frac{\delta}{2}$ and $\|\mu\|e^{\epsilon t}>2\delta$.
    Then $\omega\in \mathcal{A}_t(\epsilon),$ for each $t>S:=\max\{S_1,S_2\}$. 
    This implies that $\omega \in \liminf_{t\rightarrow \infty}\mathcal{A}_t(\epsilon):=\cup_{s>0}\cap_{t\geq s}\mathcal{A}_t(\epsilon)$. 
    According to \cite{LSR}, $D^c=\{H_{\infty}>0\}\cap\{\lim_{t\rightarrow \infty} H_t=H_{\infty}\}, \mathbb{P}_{\mu}$-a.s.. Using this we get the desired result.
\end{proof}
}
\begin{lem}\label{lemma33}

Let $f\in \mathcal{P}$. 
Assume that $\alpha\beta\leq \kappa_fb(1+\beta)$.
Then for any  \deleted{$k\in\mathbb{N}$} \added{$k\geq 0$} and $\mu \in \mathcal{M}_c(\mathbb{R}^d)$, under $\mathbb{P}_{\mu}(\cdot | D ^c)$, we have
 \begin{align}
      \frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})}\xrightarrow{d}\zeta_k, \quad t\rightarrow \infty, \label{limitdistribution1}
 \end{align}
 where $\zeta_k$ is a $(1+\beta)$-stable random variable with characteristic function
 $$\mathbb{E}(e^{i\theta\zeta_k})=\exp(e^{\alpha}m_k[\theta f]),\quad \theta \in \mathbb R.$$
 \end{lem}

 \begin{proof}
For each $\theta \in \mathbb{R}$, let $\tilde{\theta}_{t,k}=\frac{\theta}{F_k(X_{t-k-1})}$. For any \deleted{$k\in\mathbb{N}$} \added{$k\geq 0$} and $t>k+1$, we have
{\bf Zhenyao: Could you change $k\in \mathbb N$ to $k>0$ universilly?}
         \begin{align}
        &\mathbb{P}_{\mu}\big[\exp(i\theta\frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})\big|\mathscr{F}_{t-k-1}\big]\\
        &\added{ = ...}\\
        &=\exp\big(\langle U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-i\tilde{\theta}_{t,k}\langle T_{k+1}^{\alpha}f, X_{t-k-1}\rangle\big).\\
        \label{condition mean}
        &=\exp\big(\langle U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle+\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle\big)\\
       \end{align}
         Fix $\gamma_0\in (0,\beta)$, let $p=\min\{b,\frac{\alpha\gamma_0}{2(1+\gamma_0)}\}$ and $\epsilon_0=\min\{\frac{\alpha\beta}{2(1+2\beta)},\frac{p}{2}\}$.
       To get the conclusion of Lemma \ref{lemma33}, it suffices to show that
       \begin{align}
           \mathbb{P}_{\mu}\Big(\exp(i\theta\frac{I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1}}))\mathbf{1}_{D^c}\Big)\xrightarrow{t\rightarrow \infty}\mathbb{P}_{\mu}(D^c)\exp(e^{\alpha}m_k[\theta f]).
       \end{align}
     Equivalently, by Lemma \ref{lemma32}, we just need to prove
     \begin{align}
        \Big|\mathbb{P}_{\mu}\Big[\big(\exp(i\theta \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big]\Big|\xrightarrow{t\rightarrow\infty} 0.
    \end{align}
    {\bf Zhenyao: Give more detail about the above assertion. For example, We used the fact that $\exp(e^{\alpha}m_k[\theta f])$ is bounded.}

      According to \eqref{condition mean},
    \begin{align}
        &\Big|\mathbb{P}_{\mu}\Big[\big(\exp(i\theta \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big]\Big|\\
        &=\Big|\mathbb{P}_{\mu}\Big[\mathbb{P}_{\mu}\Big(\big(\exp(i\theta \frac {I_{t-k-1}^{t-k}[\langle f ,X_t\rangle]}{F_k(X_{t-k-1})})-\exp(e^{\alpha}m_k[\theta f])\big)\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\Big|\mathscr{F}_{t-k-1}\Big)\Big]\Big|\\
        &\leq \mathbb{P}_{\mu}\big[\big|\langle U_1(\tilde{\theta}_{t,k}T_k^{\alpha}f)-\tilde{U}_1(\tilde{\theta}_{t,k}T_k^{\alpha}f), X_{t-k-1}\rangle\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big]\\
        \label{ineqinlem31}
        &+\mathbb{P}_{\mu}\big[\big|\langle Z_1(\tilde{\theta}_{t,k}T_k^{\alpha}f),X_{t-k-1}\rangle-e^{\alpha}m_k[\theta f]\big|\mathbf{1}_{\mathcal{A}_{t-k-1}(\epsilon_0)}\big].
    \end{align}
{\bf Zhenyao: I think the last inequality for the above assertion needs more details. It seems that it use the result that $|e^x-e^y|\leq (|e^x|\wedge |e^y|)|x-y|$ for $x,y\in \mathbb C$.  }
